---
title: "2To3"
author: "Aimin"
date: '2022-07-28'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r 2to3, echo=FALSE}

2to3 --write --nobackups DEMO/IS-Seq-2to3
pip install reindent

reindent /home/ubuntu/DEMO/IS-Seq-2to3/ISpipelineFv3_test_bwa_mem.py

pip3 install numpy

pip3 install more_itertools
pip3 install Bio

sudo apt install ncbi-blast+

conda install -c bioconda -y ea-utils

conda install -c bioconda bwa-mem2

conda install -c bioconda blat

conda install -c bioconda starcode


python -u /home/ubuntu/DEMO/IS-Seq-2to3/ISpipelineFv3_test.py -1 /home/ubuntu/DEMO/IS-Seq-2to3/data/simulationUp_R1.fq.gz -2 /home/ubuntu/DEMO/IS-Seq-2to3/data/simulationUp_R2.fq.gz -s POOL-ISA-AVRO-6-Preclin -o /home/ubuntu/DEMO/ISseqOutput -t DEMOPython3 -r /home/ubuntu/DEMO/IS-Seq-2to3/sample_research/20210121_AssociationFIle_POOL6_Preclinical.csv -u /home/ubuntu/DEMO/IS-Seq-2to3/utilsRefData/IsSeq -p /home/ubuntu/DEMO/IS-Seq-2to3/utils -a read -c nothing -q 

nohup python -u /home/ubuntu/DEMO/IS-Seq/ISpipelineFv3_test.py -1 /home/ubuntu/DEMO/IS-Seq/data/simulationUp_R1.fq.gz -2 /home/ubuntu/DEMO/IS-Seq/data/simulationUp_R2.fq.gz -s POOL-ISA-AVRO-6-Preclin -o /home/ubuntu/DEMO/ISseqOutput -t DEMO -r /home/ubuntu/DEMO/IS-Seq/sample_research/20210121_AssociationFIle_POOL6_Preclinical.csv -u /home/ubuntu/DEMO/IS-Seq/utilsRefData/IsSeq -p /home/ubuntu/DEMO/IS-Seq/utils -a read -c nothing -q 0 > logRead.txt 2>&1 &

nohup python -u /home/ubuntu/DEMO/IS-Seq-2to3/ISpipelineFv3_test.py -1 /home/ubuntu/DEMO/IS-Seq-2to3/data/simulationUp_R1.fq.gz -2 /home/ubuntu/DEMO/IS-Seq-2to3/data/simulationUp_R2.fq.gz -s POOL-ISA-AVRO-6-Preclin -o /home/ubuntu/DEMO/ISseqOutput -t DEMOPython3 -r /home/ubuntu/DEMO/IS-Seq-2to3/sample_research/20210121_AssociationFIle_POOL6_Preclinical.csv -u /home/ubuntu/DEMO/IS-Seq-2to3/utilsRefData/IsSeq -p /home/ubuntu/DEMO/IS-Seq-2to3/utils -a read -c nothing -q 0 > logTestPython3.txt 2>&1 &

diff /home/ubuntu/DEMO/ISseqOutput/DEMOpython2/CutAdapt/POOL-ISA-AVRO-6-Preclin_FB-P5-Rd1-LTR.9_FB-P7-Rd2-LC.9_final_parse_filterNo.txt /home/ubuntu/DEMO/ISseqOutput/DEMOPython3/CutAdapt/POOL-ISA-AVRO-6-Preclin_FB-P5-Rd1-LTR.9_FB-P7-Rd2-LC.9_final_parse_filterNo.txt

# python3 works now
nohup python -u /home/ubuntu/DEMO/IS-Seq-2to3/ISpipelineFv3_test.py -1 /home/ubuntu/DEMO/IS-Seq-2to3/data/simulationUp_R1.fq.gz -2 /home/ubuntu/DEMO/IS-Seq-2to3/data/simulationUp_R2.fq.gz -s POOL-ISA-AVRO-6-Preclin -o /home/ubuntu/DEMO/ISseqOutput -t DEMOPython3 -r /home/ubuntu/DEMO/IS-Seq-2to3/sample_research/20210121_AssociationFIle_POOL6_Preclinical.csv -u /home/ubuntu/DEMO/IS-Seq-2to3/utilsRefData/IsSeq -p /home/ubuntu/DEMO/IS-Seq-2to3/utils -a read -c nothing -q 0 > logTestPython3.txt 2>&1 &
  
nohup python -u /home/ubuntu/DEMO/IS-Seq-2to3/ISpipelineFv3_test.py -1 /home/ubuntu/DEMO/IS-Seq-2to3/data/simulationUp_R1.fq.gz -2 /home/ubuntu/DEMO/IS-Seq-2to3/data/simulationUp_R2.fq.gz -s POOL-ISA-AVRO-6-Preclin -o /home/ubuntu/DEMO/ISseqOutput -t DEMOPython3 -r /home/ubuntu/DEMO/IS-Seq-2to3/sample_research/20210121_AssociationFIle_POOL6_Preclinical.csv -u /home/ubuntu/DEMO/IS-Seq-2to3/utilsRefData/IsSeq -p /home/ubuntu/DEMO/IS-Seq-2to3/utils -a umi -c nothing -q 0 > logTestUmiPython3.txt 2>&1 &
  
nohup python -u /home/ubuntu/DEMO/IS-Seq-2to3/ISpipelineFv3_test.py -1 /home/ubuntu/DEMO/IS-Seq-2to3/data/simulationUp_R1.fq.gz -2 /home/ubuntu/DEMO/IS-Seq-2to3/data/simulationUp_R2.fq.gz -s POOL-ISA-AVRO-6-Preclin -o /home/ubuntu/DEMO/ISseqOutput -t DEMOPython3 -r /home/ubuntu/DEMO/IS-Seq-2to3/sample_research/20210121_AssociationFIle_POOL6_Preclinical.csv -u /home/ubuntu/DEMO/IS-Seq-2to3/utilsRefData/IsSeq -p /home/ubuntu/DEMO/IS-Seq-2to3/utils -a fragment -c nothing -q 0 > logTestFragmentPython3.txt 2>&1 &
  
```

``````{r mixISwithNoise, echo=FALSE}

Rscript /home/ubuntu/DEMO/IS-Seq/R/makeREFIndex.R -i https://ftp.ebi.ac.uk/pub/databases/gencode/Gencode_human/release_40/GRCh38.primary_assembly.genome.fa.gz -g https://ftp.ebi.ac.uk/pub/databases/gencode/Gencode_human/release_40/gencode.v40.annotation.gtf.gz -o /home/ubuntu/DEMO/IS-Seq/utilsRefData/IsSeq/hg38_1/GRCh38.primary_assembly.genome.fa


nohup python -u /home/ubuntu/DEMO/IS-Seq/ISpipelineFv3_test.py -1 /home/ubuntu/DEMO/IS-Seq/data/simulationUp_R1.fq.gz -2 /home/ubuntu/DEMO/IS-Seq/data/simulationUp_R2.fq.gz -s POOL-ISA-AVRO-6-Preclin -o /home/ubuntu/DEMO/ISseqOutput -t DEMO2 -r /home/ubuntu/DEMO/IS-Seq/sample_research/20210121_AssociationFIle_POOL6_Preclinical.csv -u /home/ubuntu/DEMO/IS-Seq/utilsRefData/IsSeq -p /home/ubuntu/DEMO/IS-Seq/utils -a read -c nothing -q 0 > logRead2.txt 2>&1 &


nohup python -u /home/ubuntu/DEMO/IS-Seq/ISpipelineFv3_test.py -1 /home/ubuntu/DEMO/IS-Seq/data/simulationUp_R1.fq.gz -2 /home/ubuntu/DEMO/IS-Seq/data/simulationUp_R2.fq.gz -s POOL-ISA-AVRO-6-Preclin -o /home/ubuntu/DEMO/ISseqOutput -t DEMO2 -r /home/ubuntu/DEMO/IS-Seq/sample_research/20210121_AssociationFIle_POOL6_Preclinical.csv -u /home/ubuntu/DEMO/IS-Seq/utilsRefData/IsSeq -p /home/ubuntu/DEMO/IS-Seq/utils -a read -c nothing -q 0 > logRead2.txt 2>&1 &


nohup python -u /home/ubuntu/DEMO/IS-Seq/ISpipelineFv3_test.py -1 /home/ubuntu/SHARE/Aimin/INSPIIRED_test_output/simulationUp_muta_R1.fq.gz -2 /home/ubuntu/SHARE/Aimin/INSPIIRED_test_output/simulationUp_R2.fq.gz -s POOL-ISA-AVRO-6-Preclin -o /home/ubuntu/DEMO/ISseqOutput -t DEMOMutation -r /home/ubuntu/DEMO/IS-Seq/sample_research/20210121_AssociationFIle_POOL6_Preclinical.csv -u /home/ubuntu/DEMO/IS-Seq/utilsRefData/IsSeq -p /home/ubuntu/DEMO/IS-Seq/utils -a read -c nothing -q 0 > logReadMutation.txt 2>&1 &


nohup python -u /home/ubuntu/DEMO/IS-Seq/ISpipelineFv3_test.py -1 /home/ubuntu/SHARE/Aimin/INSPIIRED_test_output/simulationUp_muta_R1.fq.gz -2 /home/ubuntu/SHARE/Aimin/INSPIIRED_test_output/simulationUp_R2.fq.gz -s POOL-ISA-AVRO-6-Preclin -o /home/ubuntu/DEMO/ISseqOutput -t DEMOMutation -r /home/ubuntu/DEMO/IS-Seq/sample_research/20210121_AssociationFIle_POOL6_Preclinical.csv -u /home/ubuntu/DEMO/IS-Seq/utilsRefData/IsSeq -p /home/ubuntu/DEMO/IS-Seq/utils -a read -c nothing -q 0 > logReadMutation.txt 2>&1 &


nohup python -u /home/ubuntu/DEMO/IS-Seq/ISpipelineFv3_test.py -1 /home/ubuntu/SHARE/Aimin/INSPIIRED_test_output/simulationUp_muta5_R1.fq.gz -2 /home/ubuntu/SHARE/Aimin/INSPIIRED_test_output/simulationUp_R2.fq.gz -s POOL-ISA-AVRO-6-Preclin -o /home/ubuntu/DEMO/ISseqOutput -t DEMOMutation5 -r /home/ubuntu/DEMO/IS-Seq/sample_research/20210121_AssociationFIle_POOL6_Preclinical.csv -u /home/ubuntu/DEMO/IS-Seq/utilsRefData/IsSeq -p /home/ubuntu/DEMO/IS-Seq/utils -a read -c nothing -q 0 > logReadMutation.txt 2>&1 &

/home/ubuntu/SHARE/Aimin/INSPIIRED_test_output/simulationUp_muta5_R1.fq.gz

cat /home/ubuntu/SHARE/Aimin/INSPIIRED_test_output/simulationUp_muta5_R1.fq.gz /home/ubuntu/SHARE/Aimin/RandomFragment/RandomFragmentRandom_R1.fq.gz > /home/ubuntu/SHARE/Aimin/RandomFragment/PosRandom_R1.fq.gz

cat /home/ubuntu/SHARE/Aimin/INSPIIRED_test_output/simulationUp_R2.fq.gz /home/ubuntu/SHARE/Aimin/RandomFragment/RandomFragmentRandomR2.fq.gz > /home/ubuntu/SHARE/Aimin/RandomFragment/PosRandom_R2.fq.gz


nohup python -u /home/ubuntu/DEMO/IS-Seq/ISpipelineFv3_test.py -1 /home/ubuntu/SHARE/Aimin/RandomFragment/PosRandom_R1.fq.gz -2 /home/ubuntu/SHARE/Aimin/RandomFragment/PosRandom_R2.fq.gz -s POOL-ISA-AVRO-6-Preclin -o /home/ubuntu/DEMO/ISseqOutput -t DEMOPosRandom -r /home/ubuntu/DEMO/IS-Seq/sample_research/20210121_AssociationFIle_POOL6_Preclinical.csv -u /home/ubuntu/DEMO/IS-Seq/utilsRefData/IsSeq -p /home/ubuntu/DEMO/IS-Seq/utils -a read -c nothing -q 0 > logReadPosRandom.txt 2>&1 &

```
